SVG: The Paper (2nd part of supplementary material)

### 2022-06-07 Analysis/index2.Rmd
more arni

```{r, echo = TRUE}
# read in data
d <- read_csv("data/human_data_2014_prox.csv", show_col_types = FALSE) %>%
  mutate(condition = as_factor(condition),
         condition = fct_recode(condition, feature = "1", conjunction = "2"),
         targ_type = as_factor(targ_type))
```

We will use the model fit as detailed in @clarke2020compbio. For simplicity sake, we will characterise all of our estimated posterior probability densities with just the mean value. This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.

@@

```{r echo = TRUE}
# item weights pre-computed - see scripts/extract_item_weights_using_model.R
a <- readRDS("scratch/kristjansson_model_weights.rda") %>%
  filter(found != 1) # remove initial selections

@@

We can then plot this data to show how our ability to predict which target will be selected next varies throughout a trial. We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable.

@@

plt_a
```

@@

```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
# computed in xxxx.R
fit <- readRDS("scratch/kristjansson_model_fit.rda") %>%
  full_join(a_acc, by = c("observer", "condition")) %>%
  mutate(is_outlier = if_else(observer %in% c(35, 45), TRUE, FALSE))

@@

We can also see if the other parameters have an effect.

@@

Previous work (cite Clarke and Tatler etc) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution. Here we explore using a similar idea to account for starting locations.

```{r echo = TRUE}
# Reimport data again (as we removed the initial target selection earlier)
d <- read_csv("data/human_data_2014_prox.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))
```

>>>>

```{r, echo = TRUE}
# read in data
d <- read_csv("data/test_arni.csv", show_col_types = FALSE) %>%
  mutate(condition = as_factor(condition),
         condition = fct_recode(condition, feature = "1", conjunction = "2"),
         targ_type = as_factor(targ_type))
```

Here, we have used half the data as a training set which we used to fit the initial model. This is then used for computing model weights for the test dataset.

For simplicity's sake, we will characterise all of our estimated posterior probability densities with just the mean value. This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.

@@

```{r echo = TRUE}
# item weights pre-computed - see scripts/extract_item_weights_using_model.R
a <- readRDS("scratch/kristjansson_model_weights_train.rda") %>%
  filter(found != 1) # remove initial selections

@@

We can then plot this data to show how our ability to predict which target will be selected next varies throughout a trial. We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable (though the distinction is less clear after the initial 20 target selections).

@@

plt_a
```
Model accuracy is quite high (though lower than for Clarke et al).

@@

```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
# computed in xxxx.R
fit <- readRDS("scratch/kristjansson_model_fit_train.rda") %>%
  full_join(a_acc, by = c("observer", "condition")) %>%
  mutate(is_outlier = if_else(observer %in% c(35, 45), TRUE, FALSE))

@@

We can also see if the other parameters have an effect - which they do seem to.

@@

Similar to Clarke et al, there is a bias towards starting in a corner. Interestingly, there isn't much evidence of a central bias (possibly because these trials were completed on an iPad).

```{r echo = TRUE}
# Reimport data again (as we removed the initial target selection earlier)
d <- read_csv("data/test_arni.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))
```
